A Large-Scale Study of the Use of Eval in R

### 2020-08-28 inst/paper/main.tex
Minor fixes

The pipeline begins with downloading and installing open source R packages
from CRAN for the corpus along with their dependencies. The Kaggle programs
are downloaded from \href{http://www.kaggle.com}{Kaggle} separately by a
crawler.  Next, code size and coverage metrics from the installed packages
are extracted using the \href{ https://github.com/r-lib/covr}{\covr}
package. This is followed by extraction of runnable programs from R
packages: tests, examples and vignettes as well as from Kaggle. The code of
each extracted program is wrapped into a call to dynamic analyzer
\emph{evil} (\emph{Ev}al \emph{I}nspection \emph{L}ibrary) that collects eval
usage. The reason for this is that we only want to record eval usage for the
extracted code. Without this, the data would include eval calls from the
unit testing frameworks as well as from bootstrapping R virtual machine
itself. To avoid any interference, each program is run in its own R
instance. The \emph{evil} framework implemented as R package in 2K lines of
R and 400 lines of C++ code.

@@

We have selected the TOP \CorpusPackages packages based on their reverse
dependencies, \ie how many other packages depend on them.\footnote{Extracted
  from package metadata using a builtin function.}  This helps us find
packages which should be better written and have better code coverage.  The
resulting set contains \CorpusRCodeRnd lines of R code and
\CorpusNativeCodeRnd lines of native code.\footnote{Excluding comments and
  blank lines using \url{github.com/AlDanial/cloc}.}  For each package we
use its runnable code to compute the package code coverage.\footnote{Computed
  using \url{ https://github.com/r-lib/covr}.} On average, across the
\CorpusPackages packages, it is \CorpusMeanExprCoverage.
Figure~\ref{fig:corpus} shows these packages, the size of the dots reflects
the project's size in lines of code.  The x-axis indicates code coverage in
percents and the y-axis gives the number of call sites to \eval in log
scale. Dotted lines indicate means. Packages with over
\CorpusEvalsPackageTreshold eval call sites are named.

>>>>

The pipeline begins with downloading and installing open source R packages
from CRAN for the corpus along with their dependencies. The Kaggle programs
are downloaded from \href{http://www.kaggle.com}{Kaggle} separately by a
crawler.  Next, code size and coverage metrics from the installed packages
are extracted using the \href{ https://github.com/r-lib/covr}{\covr}
package. This is followed by extraction of runnable programs from R
packages: tests, examples and vignettes as well as from Kaggle. The code of
each extracted program is wrapped into a call to dynamic analyzer
\emph{evil} (\emph{Ev}al \emph{I}nspection \emph{L}ibrary) that collects eval
usage. The reason for this is that we only want to record eval usage for the
extracted code. Without this, the data would include eval calls from the
unit testing frameworks as well as from bootstrapping R virtual machine
itself. To avoid any interference, each program is run in its own R
instance. The \emph{evil} framework is implemented as a R package in 2K lines of
R and 400 lines of C++ code.

@@

We have selected the TOP \CorpusPackages packages based on their reverse
dependencies, \ie how many other packages depend on them.\footnote{Extracted
  from package metadata using a builtin function.}  This helps us find
packages which should be better written and have better code coverage.  The
resulting set contains \CorpusRCodeRnd lines of R code and
\CorpusNativeCodeRnd lines of native code.\footnote{Excluding comments and
  blank lines using \url{github.com/AlDanial/cloc}.}  For each package we
use its runnable code to compute the package code coverage.\footnote{Computed
  using \url{ https://github.com/r-lib/covr}.} On average, across the
\CorpusPackages packages, it is \CorpusMeanExprCoverage.
Figure~\ref{fig:corpus} shows these packages, the size of the dots reflects
the project's size in lines of code.  The x-axis indicates code coverage in
percents and the y-axis gives the number of call sites to \eval that were traced, in log
scale. Dotted lines indicate means. Packages with over
\CorpusEvalsPackageTreshold eval call sites are named.
